\documentclass[11pt,a4paper]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{geometry}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{array}
\usepackage{xcolor}
\usepackage{fancyhdr}
\usepackage{titlesec}
\usepackage{amsmath}
\usepackage{amssymb}

\geometry{margin=1in}

% Colors
\definecolor{kalshipurple}{RGB}{102, 51, 153}
\definecolor{bullgreen}{RGB}{34, 139, 34}
\definecolor{bearred}{RGB}{178, 34, 34}

% Header/Footer
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{\textcolor{kalshipurple}{Kalshi Research Report}}
\fancyhead[R]{\thepage}
\fancyfoot[C]{\small Generated on January 27, 2026}

% Section formatting
\titleformat{\section}{\Large\bfseries\color{kalshipurple}}{\thesection}{1em}{}
\titleformat{\subsection}{\large\bfseries}{\thesubsection}{1em}{}

\begin{document}

% Title
\begin{center}
    {\LARGE\bfseries\textcolor{kalshipurple}{Market Research Report}}

    \vspace{0.5cm}

    {\Large H5N1 Cases}

    \vspace{0.3cm}

    {\small Market Reference: \texttt{https://kalshi.com/markets/kxh5n1cases/h5n1-cases/kxh5n1cases-25}}
\end{center}

\vspace{1cm}

%% ============================================
\section{Market Overview}
%% ============================================

\begin{tabular}{@{}ll@{}}
    \textbf{Resolution Criteria:} & \parbox[t]{10cm}{UNKNOWN - Unable to access Kalshi market data to extract exact resolution criteria} \\[0.5em]
    \textbf{Expiration:} & UNKNOWN - Cannot determine from URL alone \\
\end{tabular}

%% ============================================
\section{Market Pricing vs Independent Estimate}
%% ============================================

\begin{center}
\begin{tabular}{lcc}
    \toprule
    \textbf{Outcome} & \textbf{Market Price} & \textbf{Independent Estimate} \\
    \midrule
    \textcolor{bullgreen}{Yes} & N/A\% & N/A\% \\
    \textcolor{bearred}{No} & N/A\% & N/A\% \\
    \bottomrule
\end{tabular}
\end{center}

\vspace{0.5cm}

\textbf{Confidence Level:} N/A

%% ============================================
\section{Edge Analysis}
%% ============================================

No edge analysis available.

%% ============================================
\section{Research Summary}
%% ============================================

H5N1 avian influenza is currently experiencing a significant outbreak across multiple species and geographic regions. The virus has been detected in dairy cattle across 16 U.S. states since March 2024, marking the first known outbreak in cattle. Human cases remain rare but have been documented, primarily among farmworkers with direct animal contact. The CDC has confirmed 58 human cases in the U.S. as of December 2024, with most cases being mild and linked to exposure to infected poultry or dairy cattle. The virus continues to evolve, with scientists monitoring for mutations that could increase human-to-human transmission risk. Current surveillance systems include monitoring of farm workers, testing of milk supplies, and tracking of wild bird populations where H5N1 remains endemic.

\subsection*{Sources}
\begin{itemize}
    \item CDC H5N1 Bird Flu Response - Official U.S. surveillance data and case reports
    \item USDA Animal and Plant Health Inspection Service - Livestock outbreak tracking
    \item WHO Global Influenza Surveillance and Response System - International case data
    \item FDA food safety monitoring - Raw milk testing results
    \item USGS National Wildlife Health Center - Wild bird surveillance data
    \item Nature journal publications - Peer-reviewed research on H5N1 evolution
    \item State agricultural departments - Local outbreak reports and worker screening
\end{itemize}

%% ============================================
\section{Persona-Based Recommendations}
%% ============================================

\begin{center}
\begin{tabular}{|p{3cm}|p{3cm}|p{8cm}|}
    \hline
    \textbf{Persona} & \textbf{Position} & \textbf{Rationale} \\
    \hline
\end{tabular}
\end{center}

%% ============================================
\section{Scenario Analysis}
%% ============================================


%% ============================================
\section*{Disclaimer}
%% ============================================

{\small\textit{This research report is for informational purposes only and does not constitute financial advice, investment advice, or a recommendation to buy or sell any securities or prediction market contracts. Prediction markets involve risk of loss. Past performance does not guarantee future results. Always do your own research and consider your own risk tolerance before participating in any market.}}

\end{document}
