\documentclass[11pt,a4paper]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{geometry}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{array}
\usepackage{xcolor}
\usepackage{fancyhdr}
\usepackage{titlesec}
\usepackage{amsmath}
\usepackage{amssymb}

\geometry{margin=1in}

% Colors
\definecolor{kalshipurple}{RGB}{102, 51, 153}
\definecolor{bullgreen}{RGB}{34, 139, 34}
\definecolor{bearred}{RGB}{178, 34, 34}

% Header/Footer
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{\textcolor{kalshipurple}{Kalshi Research Report}}
\fancyhead[R]{\thepage}
\fancyfoot[C]{\small Generated on January 27, 2026}

% Section formatting
\titleformat{\section}{\Large\bfseries\color{kalshipurple}}{\thesection}{1em}{}
\titleformat{\subsection}{\large\bfseries}{\thesubsection}{1em}{}

\begin{document}

% Title
\begin{center}
    {\LARGE\bfseries\textcolor{kalshipurple}{Market Research Report}}

    \vspace{0.5cm}

    {\Large Will Kraken go public by January 1, 2027?}

    \vspace{0.3cm}

    {\small Market Reference: \texttt{https://kalshi.com/markets/kxkrakenbankpublic/kraken-ipo/kxkrakenbankpublic-27jan01}}
\end{center}

\vspace{1cm}

%% ============================================
\section{Market Overview}
%% ============================================

\begin{tabular}{@{}ll@{}}
    \textbf{Resolution Criteria:} & \parbox[t]{10cm}{UNKNOWN - Unable to fetch exact resolution criteria from Kalshi API. Based on market title, likely resolves Yes if Kraken (cryptocurrency exchange) becomes a publicly traded company by January 1, 2027, but exact mechanics unclear.} \\[0.5em]
    \textbf{Expiration:} & 2027-01-01 \\
\end{tabular}

%% ============================================
\section{Market Pricing vs Independent Estimate}
%% ============================================

\begin{center}
\begin{tabular}{lcc}
    \toprule
    \textbf{Outcome} & \textbf{Market Price} & \textbf{Independent Estimate} \\
    \midrule
    \textcolor{bullgreen}{Yes} & N/A\% & 35.0\% \\
    \textcolor{bearred}{No} & N/A\% & 65.0\% \\
    \bottomrule
\end{tabular}
\end{center}

\vspace{0.5cm}

\textbf{Confidence Level:} Medium

%% ============================================
\section{Edge Analysis}
%% ============================================

Analysis impossible without market pricing data. However, the 35\% Yes probability suggests a relatively bearish view on Kraken's IPO prospects within the 2.5-year timeframe. If market pricing implies higher probability (say 50\%+), there could be value in fading the Yes outcome. Conversely, if market is pricing Yes below 25\%, there might be value despite regulatory headwinds.

%% ============================================
\section{Research Summary}
%% ============================================

Kraken, founded in 2011, is one of the largest cryptocurrency exchanges globally and has been considering going public for several years. The company has taken several steps that typically precede an IPO, including hiring investment banks, achieving significant revenue milestones, and expanding internationally. However, the crypto market's volatility and regulatory uncertainty have created challenges for crypto companies pursuing public offerings. Kraken faces regulatory scrutiny in multiple jurisdictions and has had to adapt its business model accordingly. The company's path to going public will likely depend on market conditions, regulatory clarity, and the overall health of the cryptocurrency sector between now and 2027.

\subsection*{Sources}
\begin{itemize}
    \item Reuters and Bloomberg - IPO preparation reporting (2021-2022)
    \item SEC official press releases - enforcement actions and settlements
    \item Kraken official company blog and website - corporate announcements
    \item TechCrunch and crypto industry publications - funding rounds and valuation data
    \item Financial Times - crypto exchange regulatory coverage
    \item CoinDesk - industry analysis and regulatory developments
    \item Company employment data from layoff announcements
    \item Japan FSA announcements regarding exchange operations
\end{itemize}

%% ============================================
\section{Persona-Based Recommendations}
%% ============================================

\begin{center}
\begin{tabular}{|p{3cm}|p{3cm}|p{8cm}|}
    \hline
    \textbf{Persona} & \textbf{Position} & \textbf{Rationale} \\
    \hline
        Risk Averse & No position until market pricing becomes available & Without market pricing data, there's no way to identify a clear edge or assess whether the 35\% Yes p... \\
        \hline
        Risk Seeking & Consider betting Yes if market pricing implies <25\% probability & The 2.5-year timeframe provides multiple pathways for Kraken to go public, and crypto exchanges have... \\
        \hline
        News Driven & Wait for catalyst-driven entry after regulatory clarity & This market will be heavily influenced by regulatory developments, SEC enforcement actions, and cryp... \\
        \hline
        Macro Thinker & Consider No position as crypto regulatory hedge & A Kraken IPO failure could correlate with broader crypto regulatory crackdowns, making this a potent... \\
        \hline
        Casual Participant & Pass until market pricing provides clearer opportunity & Without knowing if 35\% represents good or bad value, this market requires too much research into reg... \\
        \hline
        Data Analyst & No position - insufficient quantitative edge & Without market pricing for comparison, there's no statistical edge to identify. The 35\% estimate lac... \\
        \hline
\end{tabular}
\end{center}

%% ============================================
\section{Scenario Analysis}
%% ============================================

    \subsection*{Best Case}
    Crypto market enters sustained bull run by 2025, with clear regulatory framework established in US. Kraken completes compliance preparations, demonstrates strong financials with \$500M+ annual revenue, and successfully goes public via traditional IPO in Q2-Q3 2026. Strong institutional demand and retail crypto adoption drive valuation above \$10B.

    \textbf{Probability Shift:} Yes probability increases to 60-70\% as regulatory clarity emerges and crypto markets recover

    \textbf{Key Triggers:}
    \begin{itemize}
            \item Bitcoin ETF approval drives institutional adoption
            \item Comprehensive crypto regulation passed by Congress
            \item Kraken announces IPO filing with strong financial metrics
            \item Sustained crypto bull market above previous highs
    \end{itemize}

    \subsection*{Worst Case}
    Prolonged crypto winter continues through 2025-2026, with trading volumes and revenues declining. Additional regulatory crackdowns or enforcement actions against major exchanges create hostile environment. Kraken focuses on private funding rounds and international expansion instead of US public offering, or faces operational challenges that delay IPO indefinitely.

    \textbf{Probability Shift:} Yes probability drops to 10-15\% as regulatory environment deteriorates and market conditions remain unfavorable

    \textbf{Key Triggers:}
    \begin{itemize}
            \item Major crypto exchange faces SEC enforcement action
            \item Extended bear market with Bitcoin below \$30K through 2025
            \item Stricter exchange regulations requiring significant compliance costs
            \item Kraken announces focus on private markets or international listing
    \end{itemize}

    \subsection*{Most Likely}
    Mixed crypto market conditions with moderate recovery by 2025-2026. Regulatory environment slowly clarifies but remains complex. Kraken makes progress on compliance and financials but faces typical IPO delays and market timing challenges. Either goes public in very late 2026/early 2027 (close call for resolution) or pushes IPO to 2027-2028 due to market conditions or preparation needs.

    \textbf{Probability Shift:} Yes probability remains around 30-40\% reflecting uncertainty about timing rather than viability

    \textbf{Key Triggers:}
    \begin{itemize}
            \item Gradual crypto market recovery without clear breakout
            \item Piecemeal regulatory guidance rather than comprehensive framework
            \item Kraken shows progress but faces normal IPO timeline extensions
            \item Other crypto companies test public market reception first
    \end{itemize}


%% ============================================
\section*{Disclaimer}
%% ============================================

{\small\textit{This research report is for informational purposes only and does not constitute financial advice, investment advice, or a recommendation to buy or sell any securities or prediction market contracts. Prediction markets involve risk of loss. Past performance does not guarantee future results. Always do your own research and consider your own risk tolerance before participating in any market.}}

\end{document}
