\documentclass[11pt,a4paper]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{geometry}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{array}
\usepackage{xcolor}
\usepackage{fancyhdr}
\usepackage{titlesec}
\usepackage{amsmath}
\usepackage{amssymb}

\geometry{margin=1in}

% Colors
\definecolor{kalshipurple}{RGB}{102, 51, 153}
\definecolor{bullgreen}{RGB}{34, 139, 34}
\definecolor{bearred}{RGB}{178, 34, 34}

% Header/Footer
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{\textcolor{kalshipurple}{Kalshi Research Report}}
\fancyhead[R]{\thepage}
\fancyfoot[C]{\small Generated on January 27, 2026}

% Section formatting
\titleformat{\section}{\Large\bfseries\color{kalshipurple}}{\thesection}{1em}{}
\titleformat{\subsection}{\large\bfseries}{\thesubsection}{1em}{}

\begin{document}

% Title
\begin{center}
    {\LARGE\bfseries\textcolor{kalshipurple}{Market Research Report}}

    \vspace{0.5cm}

    {\Large Will New Jersey Drone Sightings be confirmed?}

    \vspace{0.3cm}

    {\small Market Reference: \texttt{https://kalshi.com/markets/kxnjdrones/nj-drones/kxnjdrones-25}}
\end{center}

\vspace{1cm}

%% ============================================
\section{Market Overview}
%% ============================================

\begin{tabular}{@{}ll@{}}
    \textbf{Resolution Criteria:} & \parbox[t]{10cm}{If the New Jersey Drone Sightings is confirmed by any of the Source Agencies after August 12, 2025 and before Jan 1, 2026, then the market resolves to Yes.} \\[0.5em]
    \textbf{Expiration:} & 2026-01-01T15:00:00Z \\
\end{tabular}

%% ============================================
\section{Market Pricing vs Independent Estimate}
%% ============================================

\begin{center}
\begin{tabular}{lcc}
    \toprule
    \textbf{Outcome} & \textbf{Market Price} & \textbf{Independent Estimate} \\
    \midrule
    \textcolor{bullgreen}{Yes} & 50.0\% & 15.0\% \\
    \textcolor{bearred}{No} & 50.0\% & 85.0\% \\
    \bottomrule
\end{tabular}
\end{center}

\vspace{0.5cm}

\textbf{Confidence Level:} Medium

%% ============================================
\section{Edge Analysis}
%% ============================================

Strong edge appears to exist on the 'No' outcome. Market is treating this as pure uncertainty (50/50) rather than incorporating base rates from historical UAP investigations and current agency assessments. The gap is too large (35\%) to be explained by normal market noise, especially given the clear official messaging pattern.

%% ============================================
\section{Research Summary}
%% ============================================

The New Jersey drone sightings refer to widespread reports of unidentified aerial phenomena observed across New Jersey and surrounding areas starting in late November 2024. Multiple federal agencies including the FBI, FAA, DHS, and Pentagon have been investigating these incidents. Official statements have consistently indicated that most sightings are likely misidentified conventional aircraft, though investigations remain ongoing. The phenomena has generated significant public attention and political pressure for transparency, with bipartisan calls for disclosure from elected officials. Key challenges include the volume of reports (hundreds), difficulty distinguishing genuine anomalies from conventional aircraft, and the politically sensitive nature of UAP investigations following recent congressional hearings on the topic.

\subsection*{Sources}
\begin{itemize}
    \item FBI Newark Field Office - Official statements on ongoing drone investigation
    \item Federal Aviation Administration - Public announcements and flight restrictions
    \item Pentagon Press Secretary statements - Official DOD position on investigations
    \item New Jersey Governor's Office - Public statements and press conferences
    \item Department of Homeland Security - Official coordination communications
    \item Congressional members' public statements - Bipartisan calls for transparency
    \item Pentagon's AARO (All-domain Anomaly Resolution Office) - Historical UAP investigation outcomes
\end{itemize}

%% ============================================
\section{Persona-Based Recommendations}
%% ============================================

\begin{center}
\begin{tabular}{|p{3cm}|p{3cm}|p{8cm}|}
    \hline
    \textbf{Persona} & \textbf{Position} & \textbf{Rationale} \\
    \hline
        Risk Averse & Large position on 'No' outcome & The 35\% edge on 'No' offers exactly what risk-averse participants seek: high confidence in a favorab... \\
        \hline
        Risk Seeking & Small contrarian position on 'Yes' outcome & While the analysis suggests 'No' is mispriced, risk-seeking participants might find the asymmetric p... \\
        \hline
        News Driven & Staged position on 'No' with readiness to pivot & News-driven participants should focus on upcoming catalysts: congressional hearings, agency briefing... \\
        \hline
        Macro Thinker & Moderate position on 'No' as part of broader UAP portfolio & This market fits into a larger pattern of UAP-related predictions where public imagination consisten... \\
        \hline
        Casual Participant & Simple position on 'No' outcome & The thesis is straightforward: 'Government says normal stuff, probably is normal stuff.' This fits t... \\
        \hline
        Data Analyst & Conservative position on 'No' with systematic tracking & The 35\% gap exceeds typical market inefficiency ranges, suggesting a genuine mispricing rather than ... \\
        \hline
\end{tabular}
\end{center}

%% ============================================
\section{Scenario Analysis}
%% ============================================

    \subsection*{Best Case}
    Federal agencies complete their investigation by Q2 2025 and issue definitive statements that all sightings have conventional explanations (aircraft, drones, celestial objects). Media coverage shifts to debunking mode, public interest wanes, and no new significant sightings occur. The investigation follows the typical UAP pattern where initial mystery gives way to prosaic explanations.

    \textbf{Probability Shift:} No confirmation probability increases to 90-95\%

    \textbf{Key Triggers:}
    \begin{itemize}
            \item FBI/DHS joint statement identifying specific conventional sources
            \item Release of radar/flight data showing commercial/military aircraft correlation
            \item Demonstration of misidentified celestial events during peak sighting times
            \item Decline in new sighting reports by March 2025
    \end{itemize}

    \subsection*{Worst Case}
    Investigation uncovers genuinely anomalous objects that cannot be explained conventionally. Physical evidence is recovered, sensor data confirms non-conventional flight characteristics, or foreign adversary technology is definitively identified. Government agencies are forced to acknowledge something genuinely unexplained occurred, meeting the resolution criteria.

    \textbf{Probability Shift:} No confirmation probability drops to 60-70\%

    \textbf{Key Triggers:}
    \begin{itemize}
            \item Recovery of physical debris with unexplained materials or technology
            \item Multi-sensor confirmation of objects displaying impossible flight characteristics
            \item Official admission by DoD/intelligence agencies of foreign technology beyond known capabilities
            \item Whistleblower revelations with verified evidence of cover-up
    \end{itemize}

    \subsection*{Most Likely}
    Investigation continues with mixed but inconclusive results. Most sightings receive conventional explanations, but a few remain unexplained due to insufficient data rather than genuinely anomalous characteristics. Agencies maintain their current stance that nothing suggests non-conventional origins, avoiding definitive 'confirmation' while acknowledging some cases lack complete explanations.

    \textbf{Probability Shift:} No confirmation probability remains at 80-85\%

    \textbf{Key Triggers:}
    \begin{itemize}
            \item Partial explanations for majority of sightings by agencies
            \item A few cases remain 'unresolved' but not confirmed as anomalous
            \item Continued official messaging emphasizing conventional explanations
            \item Gradual decrease in new reports without dramatic revelations
    \end{itemize}


%% ============================================
\section*{Disclaimer}
%% ============================================

{\small\textit{This research report is for informational purposes only and does not constitute financial advice, investment advice, or a recommendation to buy or sell any securities or prediction market contracts. Prediction markets involve risk of loss. Past performance does not guarantee future results. Always do your own research and consider your own risk tolerance before participating in any market.}}

\end{document}
