\documentclass[11pt,a4paper]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{geometry}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{array}
\usepackage{xcolor}
\usepackage{fancyhdr}
\usepackage{titlesec}
\usepackage{amsmath}
\usepackage{amssymb}

\geometry{margin=1in}

% Colors
\definecolor{kalshipurple}{RGB}{102, 51, 153}
\definecolor{bullgreen}{RGB}{34, 139, 34}
\definecolor{bearred}{RGB}{178, 34, 34}

% Header/Footer
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{\textcolor{kalshipurple}{Kalshi Research Report}}
\fancyhead[R]{\thepage}
\fancyfoot[C]{\small Generated on January 27, 2026}

% Section formatting
\titleformat{\section}{\Large\bfseries\color{kalshipurple}}{\thesection}{1em}{}
\titleformat{\subsection}{\large\bfseries}{\thesubsection}{1em}{}

\begin{document}

% Title
\begin{center}
    {\LARGE\bfseries\textcolor{kalshipurple}{Market Research Report}}

    \vspace{0.5cm}

    {\Large Will Tesla announce a gas car this year?}

    \vspace{0.3cm}

    {\small Market Reference: \texttt{https://kalshi.com/markets/kxteslagas/tesla-gas-car/kxteslagas-25}}
\end{center}

\vspace{1cm}

%% ============================================
\section{Market Overview}
%% ============================================

\begin{tabular}{@{}ll@{}}
    \textbf{Resolution Criteria:} & \parbox[t]{10cm}{If Tesla has announced the development of an automobile (including cars, trucks, but not a motor cycle, e.g.) that can use gasoline to power a combustion engine inside of it that will at least partially power the car before Jan 1, 2026, then the market resolves to Yes.} \\[0.5em]
    \textbf{Expiration:} & 2025-12-31T15:00:00Z \\
\end{tabular}

%% ============================================
\section{Market Pricing vs Independent Estimate}
%% ============================================

\begin{center}
\begin{tabular}{lcc}
    \toprule
    \textbf{Outcome} & \textbf{Market Price} & \textbf{Independent Estimate} \\
    \midrule
    \textcolor{bullgreen}{Yes} & 50.0\% & 2.0\% \\
    \textcolor{bearred}{No} & 50.0\% & 98.0\% \\
    \bottomrule
\end{tabular}
\end{center}

\vspace{0.5cm}

\textbf{Confidence Level:} High

%% ============================================
\section{Edge Analysis}
%% ============================================

Massive edge appears to exist on the 'No' side. The market's 50/50 pricing suggests either: (1) participants don't understand Tesla's business model, (2) this is a low-information entertainment market, or (3) there's some insider information about a shocking strategic pivot. Given Tesla's \$100B+ market cap built on EV leadership and sustainable energy mission, a gas car announcement would be corporate suicide. The 48 percentage point gap is so large it suggests market inefficiency rather than hidden information.

%% ============================================
\section{Research Summary}
%% ============================================

Tesla's business model and corporate identity have been fundamentally built around electric vehicle technology and sustainable transportation since its founding in 2003. The company's mission statement explicitly focuses on 'accelerating the world's transition to sustainable energy.' CEO Elon Musk has repeatedly made strong public statements against internal combustion engines, calling them outdated technology and emphasizing Tesla's commitment to electric-only vehicles. Tesla has invested billions in electric vehicle infrastructure, including Supercharger networks, battery technology (Gigafactories), and electric powertrain development. The company's recent strategic moves continue to reinforce this electric-only approach, including partnerships focused on charging infrastructure and battery technology. However, the automotive industry has seen some companies adopt hybrid strategies or diversify their portfolios in response to market conditions, though Tesla has shown no indication of such strategic shifts.

\subsection*{Sources}
\begin{itemize}
    \item Tesla official website and mission statement
    \item Tesla SEC filings and annual reports (10-K forms) 2023-2024
    \item Tesla earnings call transcripts Q1-Q4 2024
    \item Reuters automotive industry coverage 2024
    \item Bloomberg Tesla corporate strategy analysis
    \item Elon Musk verified social media statements and interviews 2023-2024
    \item Tesla Investor Relations press releases 2024
\end{itemize}

%% ============================================
\section{Persona-Based Recommendations}
%% ============================================

\begin{center}
\begin{tabular}{|p{3cm}|p{3cm}|p{8cm}|}
    \hline
    \textbf{Persona} & \textbf{Position} & \textbf{Rationale} \\
    \hline
        Risk Averse & Strong 'No' position with significant allocation & This appears to be one of the highest-confidence edges available - Tesla announcing a gas car would ... \\
        \hline
        Risk Seeking & Small speculative 'Yes' position as lottery ticket & While the base case strongly favors 'No', the massive mispricing could indicate hidden information o... \\
        \hline
        News Driven & Wait for catalyst clarity before entering & The extreme mispricing suggests either hidden information or market dysfunction. News-driven partici... \\
        \hline
        Macro Thinker & Moderate 'No' position as EV sector hedge & This market reflects broader misconceptions about EV transition momentum. A 'No' position aligns wit... \\
        \hline
        Casual Participant & Simple 'No' position with entertainment value & Easy thesis to remember: Tesla = electric cars, period. Elon Musk has built his entire brand on sust... \\
        \hline
        Data Analyst & No position until market mechanics are understood & The 48 percentage point gap is statistically suspicious and warrants investigation before position e... \\
        \hline
\end{tabular}
\end{center}

%% ============================================
\section{Scenario Analysis}
%% ============================================

    \subsection*{Best Case}
    Tesla continues its EV-focused strategy without any gas car announcements. The company doubles down on its sustainable energy mission, potentially announcing new EV models, battery breakthroughs, or expanded charging infrastructure. Market gradually corrects to reflect the near-impossibility of a gas car announcement, with 'No' probability rising to 95\%+.

    \textbf{Probability Shift:} Market corrects from 50\% to 95\%+ for 'No' outcome as more informed traders enter

    \textbf{Key Triggers:}
    \begin{itemize}
            \item Tesla announces new EV models or battery tech
            \item Musk makes strong anti-gas statements
            \item Informed traders arbitrage the mispricing
            \item Market gains more sophisticated participants
    \end{itemize}

    \subsection*{Worst Case}
    Tesla makes a shocking strategic announcement that involves some form of hybrid or gas-powered vehicle, potentially as part of a legacy automaker partnership, emergency market response, or completely unexpected pivot. This could include acquiring a traditional automaker with gas vehicles or announcing a hybrid as a 'bridge technology' despite contradicting years of company messaging.

    \textbf{Probability Shift:} Market was actually correct at 50\%, proving the edge analysis was wrong

    \textbf{Key Triggers:}
    \begin{itemize}
            \item Unexpected Tesla partnership with traditional automaker
            \item Major shift in EV market conditions
            \item Regulatory changes favoring combustion engines
            \item Previously unknown Tesla project revelation
    \end{itemize}

    \subsection*{Most Likely}
    Tesla makes no gas car announcements and continues EV focus, but market remains inefficient due to its entertainment/novelty nature. Probability stays irrationally close to 50/50 throughout most of the year, with only modest correction toward 'No' as resolution approaches. Market efficiency is limited by participant pool and low stakes.

    \textbf{Probability Shift:} Modest correction to 60-70\% for 'No' by year-end, but significant mispricing persists

    \textbf{Key Triggers:}
    \begin{itemize}
            \item Continued absence of any gas car hints
            \item Tesla's regular EV-focused announcements
            \item Market remains primarily entertainment-focused
            \item Limited arbitrage activity due to platform constraints
    \end{itemize}


%% ============================================
\section*{Disclaimer}
%% ============================================

{\small\textit{This research report is for informational purposes only and does not constitute financial advice, investment advice, or a recommendation to buy or sell any securities or prediction market contracts. Prediction markets involve risk of loss. Past performance does not guarantee future results. Always do your own research and consider your own risk tolerance before participating in any market.}}

\end{document}
